Julianna's algal metrics wrangling code

### 2024-08-16 julianna_algalMetric_wrangling.Rmd
Making a clean script for Aug 29 figgies that only uses standardized dataset

```{r}
noamallTime <- read_csv(here("data/algae_diversity_stability_metrics_alltime.csv"))
```

```{r}
noamallTime %>% 
  select(site, habitat, island_side, algae_shannon_stability, algae_loreau_mean, algae_loreau_se, algae_portfolio_mean, algae_portfolio_se) %>% 
  full_join(alltimeCV) -> alltimeJoin
```

>>>>

```{r}
noamallTime <- read_csv(here("data/NOAMalgae_diversity_stability_metrics_alltime.csv"))
```

```{r}
noamallTime %>% 
  select(site, habitat, island_side, algae_shannon_stability, loreau_synchrony, portfolio_effect) %>% 
  full_join(alltimeCV) -> alltimeJoin
```
